Results

### 2020-01-21 analysis/02_analysis.Rmd
Change width of figures

```{r causal-dag, fig.width=10/3, fig.height=2}
theory_dag <- dagify(Y ~ I + C + F,
                     C ~ I + F,
                     outcome = "Y",
                     exposure = "C") %>% 
  tidy_dagitty(layout = "sugiyama")

@@

plot_dag %T>% 
  print() %T>%
  ggsave(., filename = here("analysis", "output", "figures", "causal-path.pdf"),
         width = 10/3, height = 2, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("analysis", "output", "figures", "causal-path.png"),
         width = 10/3, height = 2, units = "in", type = "cairo", dpi = 300)
```

@@

```{r plot-likely-diffs, warning=FALSE, fig.width=10/3, fig.height=5.5}
tidied_diffs_likely <- all_models_likely %>% 
  unnest(posterior_chains_long) %>% 
  filter(.variable == "theta_diff") %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  mutate(title = str_remove(title, " \\| Crackdown"))

@@

plot_diffs_likely_all %T>% 
  ggsave(., filename = here("analysis", "output", "figures", "likely-diffs.pdf"),
         width = 10/3, height = 5.5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("analysis", "output", "figures", "likely-diffs.png"),
         width = 10/3, height = 5.5, units = "in", type = "cairo", dpi = 300)
```

@@

```{r plot-amount-diffs, warning=FALSE, fig.width=10/3, fig.height=5.5}
# This will generate a warning because unnest() puts the crackdown values into
# one column and we cheated by renaming issue and funding as crackdown, so it
# gets mad when combining the factors in crackdown with those in issue and
# funding. But because we only care about the diffs, we don't actually need the
# category labels here, so it's all good.
tidied_diffs_amount <- all_models_amount %>% 
  unnest(posterior_chains_long) %>% 
  filter(.variable == "mu_diff") %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  mutate(title = str_remove(title, " \\| Crackdown"))

@@

plot_diffs_amounts_all %T>% 
  ggsave(., filename = here("analysis", "output", "figures", "amount-diffs.pdf"),
         width = 10/3, height = 5.5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("analysis", "output", "figures", "amount-diffs.png"),
         width = 10/3, height = 5.5, units = "in", type = "cairo", dpi = 300)
```

>>>>

```{r causal-dag, fig.width=4.75, fig.height=2}
theory_dag <- dagify(Y ~ I + C + F,
                     C ~ I + F,
                     outcome = "Y",
                     exposure = "C") %>% 
  tidy_dagitty(layout = "sugiyama")

@@

plot_dag %T>% 
  print() %T>%
  ggsave(., filename = here("analysis", "output", "figures", "causal-path.pdf"),
         width = 4.75, height = 2, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("analysis", "output", "figures", "causal-path.png"),
         width = 4.75, height = 2, units = "in", type = "cairo", dpi = 300)
```

@@

```{r plot-likely-diffs, warning=FALSE, fig.width=4.75, fig.height=5.5}
tidied_diffs_likely <- all_models_likely %>% 
  unnest(posterior_chains_long) %>% 
  filter(.variable == "theta_diff") %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  mutate(title = str_remove(title, " \\| Crackdown"))

@@

plot_diffs_likely_all %T>% 
  ggsave(., filename = here("analysis", "output", "figures", "likely-diffs.pdf"),
         width = 4.75, height = 5.5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("analysis", "output", "figures", "likely-diffs.png"),
         width = 4.75, height = 5.5, units = "in", type = "cairo", dpi = 300)
```

@@

```{r plot-amount-diffs, warning=FALSE, fig.width=4.75, fig.height=5.5}
# This will generate a warning because unnest() puts the crackdown values into
# one column and we cheated by renaming issue and funding as crackdown, so it
# gets mad when combining the factors in crackdown with those in issue and
# funding. But because we only care about the diffs, we don't actually need the
# category labels here, so it's all good.
tidied_diffs_amount <- all_models_amount %>% 
  unnest(posterior_chains_long) %>% 
  filter(.variable == "mu_diff") %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  mutate(title = str_remove(title, " \\| Crackdown"))

@@

plot_diffs_amounts_all %T>% 
  ggsave(., filename = here("analysis", "output", "figures", "amount-diffs.pdf"),
         width = 4.75, height = 5.5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("analysis", "output", "figures", "amount-diffs.png"),
         width = 4.75, height = 5.5, units = "in", type = "cairo", dpi = 300)
```
